Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-06 inspiral_svd.tex
Fixing Mireia's name
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@942 ccdd05d5-56c1-461a-bf98-85f6876523b4

\author{Kipp Cannon$^{1}$, Romain Cariou$^{2}$, Adrian Chapman$^3$, M
Crispin-Ortuzar$^4$, Nickolas Fotopoulos$^3$, Melissa Frei $^5$, Chad
Hanna$^{6}$, Erin Kara$^{7}$, Drew Keppel$^{8,9}$, Laura Liao$^{10}$, Stephen
Privitera $^3$, Antony C Searle$^3$, Leo Singer$^3$ and Alan J  Weinstein$^3$}

>>>>

\author{Kipp Cannon$^{1}$, Romain Cariou$^{2}$, Adrian Chapman$^3$, Mireia
Crisp\'{i}n-Ortuzar$^4$, Nickolas Fotopoulos$^3$, Melissa Frei $^5$, Chad
Hanna$^{6}$, Erin Kara$^{7}$, Drew Keppel$^{8,9}$, Laura Liao$^{10}$, Stephen
Privitera $^3$, Antony C Searle$^3$, Leo Singer$^3$ and Alan J  Weinstein$^3$}
